Eval expressions

### 2021-02-23 analysis/expressions.Rmd
Port normalized/minimized expression from expressions.Rmd to normalized.Rmd

---
title: "Eval expressions"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  normalized_path: normalized-expressions.fst
  corpus_path: ../corpus.fst
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

read_fst(normalized_path) %>% as_tibble() -> N

@@

# Normalization of resolved expressions

We join the normalized expressions and their statistics with the calls.

```{r}
E_cano <- E %>% left_join(N, by = c("hash" = "expr_resolved_hash")) # Common column is the hash of the full resolved expression
```

```{r}
widespread_canonic <- E_cano %>%
  group_by(expr_canonic) %>%
  summarize(n_call_sites = n_distinct(src_ref), n_packages = n_distinct(ev_package))

widespread_canonic %>%
  arrange(desc(n_call_sites)) %>%
  datatable()
```

>>>>

---
title: "Eval expressions"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  normalized_path: normalized-expressions.csv
  corpus_path: ../corpus.fst
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

@@
